---
title: "STA238 - Winter 2021"
author: "[ADD YOUR NAME HERE - STUDENT NUMBER]"
subtitle: Assignment 1
output:
  pdf_document: default
---

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(openintro)
```


# Part 1


*Exercise: <Type your CLT Question here>*


*Solution:* 

<Type your answer here>

```{r, include = TRUE}

## It is recommended that you interlace your answer in 
## Part 1b with some r code.  

## You may need more R chunks and you may want to include plots.

```

<Type more of your answer here>



\newpage

# Part 2

## Data

<Type here a paragraph introducing the data, its context and the data collection process.>

```{r, include = FALSE}

# Here you can load in and clean the data (you may need to do the cleaning in a separate R script). 

# You may need additional chunks, in case you want to include some of the cleaning output.

```

<Type here a summary of the cleaning process.>

<Include a description of the important variables.> 

```{r, include=FALSE}

# Use this to calculate some summary measures. 

```


<Include a description of the numerical summaries. Remember you can use `r ` to use inline R code.>




```{r, echo = TRUE}

# Use this to create some plots. 

```

<Include a clear description of the plot(s). I would recommend one paragraph for each plot.> 

All analysis for this report was programmed using `R version 4.0.2`. 


## Bibliography

1. Grolemund, G. (2014, July 16) *Introduction to R Markdown*. RStudio. [https://rmarkdown.rstudio.com/articles_intro.html](https://rmarkdown.rstudio.com/articles_intro.html). (Last Accessed: January 15, 2021) 

2. Dekking, F. M., et al. (2005) *A Modern Introduction to Probability and Statistics: Understanding why and how.* Springer Science & Business Media.

3.  Allaire, J.J., et. el. *References: Introduction to R Markdown*. RStudio. [https://rmarkdown.rstudio.com/docs/](https://rmarkdown.rstudio.com/docs/). (Last Accessed: January 15, 2021) 







